# Data sources

The aim of this project is to analyze the changes in the population of international students studying in the United States from various countries in recent years. The data was collected from [*All Places of Origin, Open Door*](https://opendoorsdata.org/data/international-students/all-places-of-origin/), which is sponsored by the U.S. Government and Institute of International Education. We selected international students for from 1949 to 2020 from various regions, including Africa, Asia, Europe, Latin America & Caribbean, Middle East, Oceania.

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width = 200)
```

```{r, message=FALSE}
library(readxl)
library(tidyverse)
library(stringr)
```

## General Information of Dataset
```{r}
projdata <- read_excel("Census_All-Places-of-Origin_OD21.xlsx", 
                       col_types = c("numeric", "text", "numeric", 
                                     "numeric", "numeric", "numeric", "numeric", 
                                     "numeric", "numeric", "numeric", "numeric", "numeric", 
                                     "numeric", "numeric", "numeric", "numeric", "numeric", 
                                     "numeric", "numeric", "numeric", "numeric", "numeric", 
                                     "numeric", "numeric", "numeric", "numeric", "numeric", 
                                     "numeric", "numeric", "numeric", "numeric", "numeric", 
                                     "numeric", "numeric"),
                       na = "-",
                       col_names = T)
names(projdata)[1] <- "Code of Origin"
projdata <- projdata %>%
  select(`Place of Origin`,`Code of Origin`, `1949/50`:`2020/21`)
```

```{r}
nrow(projdata)
ncol(projdata)
```

```{r, echo=FALSE}
knitr::kable(
  head(projdata[, 1:8], 4), booktabs = TRUE,
  caption = 'A table of the first 4 rows of our final project data.'
)
```

<br>

## Describtion of Variable

Based on these outputs, we can find that the raw data has the following 34 columns and 299 rows:

`Code of origin`: the region and code of each country, represented by 4 digit

`Place of origin`: the name of the continent and country researched.

`1949/50`: the number of international students in US in Academic Year 1949 - 1950

`1954/55`: the number of international students in US in Academic Year 1954 - 1955 

`1959/60`: the number of international students in US in Academic Year 1959 - 1960

`1964/65`: the number of international students in US in Academic Year 1964 - 1965

`1969/70`: the number of international students in US in Academic Year 1969 - 1970

`1974/75`: the number of international students in US in Academic Year 1974 - 1975

`1979/80`: the number of international students in US in Academic Year 1979 - 1980

`1984/85`: the number of international students in US in Academic Year 1984 - 1985

`1989/90`: the number of international students in US in Academic Year 1989 - 1990

`1994/95`: the number of international students in US in Academic Year 1994 - 1995

`1999/00`: the number of international students in US in Academic Year 1999 - 2000

`2000/01`: the number of international students in US in Academic Year 2000 - 2001

`2001/02`: the number of international students in US in Academic Year 2001 - 2002

`2002/03`: the number of international students in US in Academic Year 2002 - 2003

`2003/04`: the number of international students in US in Academic Year 2003 - 2004

`2004/05`: the number of international students in US in Academic Year 2004 - 2005

`2005/06`: the number of international students in US in Academic Year 2005 - 2006

`2006/07`: the number of international students in US in Academic Year 2006 - 2007

`2007/08`: the number of international students in US in Academic Year 2007 - 2008

`2008/09`: the number of international students in US in Academic Year 2008 - 2009

`2009/10`: the number of international students in US in Academic Year 2009 - 2010

`2010/11`: the number of international students in US in Academic Year 2010 - 2011

`2011/12`: the number of international students in US in Academic Year 2011 - 2012

`2012/13`: the number of international students in US in Academic Year 2012 - 2013

`2013/14`: the number of international students in US in Academic Year 2013 - 2014

`2014/15`: the number of international students in US in Academic Year 2014 - 2015

`2015/16`: the number of international students in US in Academic Year 2015 - 2016

`2016/17`: the number of international students in US in Academic Year 2016 - 2017

`2017/18`: the number of international students in US in Academic Year 2017 - 2018

`2018/19`: the number of international students in US in Academic Year 2018 - 2019

`2019/20`: the number of international students in US in Academic Year 2019 - 2020

`2020/21`: the number of international students in US in Academic Year 2020 - 2021

<br>


## Issue of Data set

### For missing Value

There are a lot of NAs in the dataset, but there are some that do not make sense. Because the data source is in Excel format and separating it with blank lines is a common Excel method.


### For Place of Origin
The format for countries and continents is not uniform. So, we have to modify it to the same format before analysis.




<br>
